Modern Graph Generators: A Survey

### 2018-11-25 generators_LinkedData.tex
Sherif Changes

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different datatypes and object references of various types are
used in property values. Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source. This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the most commonly used SPARQL features.

@@

\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF datasets and are mostly relational-like. Hence, they proposed a benchmark for  query processing over real graphs~\cite{sib}. The proposed benchmark simulates an RDF backend of a social network site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments. The distribution of generated data on each relation follows the data distribution inferred from real-world social networks. In addition, association rules are included in order to convey the real-world data correlation into synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload based on openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark introduces two classes of query features -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to evaluate the strengths and weaknesses of the various physical design alternatives that have been implemented by the different RDF systems. The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload. %For the study in the paper the authors generated 12,500 test queries from 125 query templates.

@@

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark simulates a media or a publishing organization that handles large amount of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities: Gaussian distribution and Zipf's power-law distribution. LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statements by assigning them with invalid domain and creating instances with no type information. The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.

>>>>

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different datatypes and object references of various types are
used in property values. Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source. This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.  For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the frequently used SPARQL features.

@@

\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF databases and are mostly focusing on the relational style aspects. Hence, they proposed a benchmark for  query evaluation using real graphs~\cite{sib}. The proposed benchmark mimics using an RDF store for a social network. \iffalse site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments.\fi The distribution of the generated data for each type follows the  distribution of the associated type inferred from real-world social networks. Additionally, association rules are exploited for representing the real-world data correlation in the generated synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload that uses openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates. \iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has been designed at the University of Waterloo. It implements stress testing tools that focus on addressing the observation that existing SPARQL benchmarks are not adequate for evaluating systems using a verity of queries and  workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark focuses on two types of query aspects -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, DBPSB, and SP$^2$Bench) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to evaluate the strengths and weaknesses of the various physical design alternatives that have been implemented by the different RDF systems. In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which follows the WatDiv schema and produces a  set of query templates, (3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload. %For the study in the paper the authors generated 12,500 test queries from 125 query templates.

@@

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark simulates a media or a publishing organization that handles large amount of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities: Gaussian distribution and Zipf's power-law distribution. LinkGen can augment the generated data with inconsistent and noisy  data such as updating a given datatype property with two conflicting values or  adding triples with syntactic errors. \iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real ones given that the end-user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.
